Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-10-04 manuscript.Rmd
update repro
fake github access in docker

    - aaronpeikert/repro@27e7d22

@@

```{r, include=FALSE}
opts <- options()
```

@@

```{r}
repro::check_git()
repro::check_make()
repro::check_docker()
```

>>>>

    - aaronpeikert/repro@15a069

@@

```{r, include=FALSE}
opts <- options()
options(repro.github = TRUE,
        repro.github.ssh = TRUE,
        repro.ssh = TRUE,
        repro.github.token = TRUE)
```

@@

```{r, include=FALSE}
opts <- options()
options(repro.github = TRUE,
        repro.github.ssh = TRUE,
        repro.github.token = TRUE)
```

```{r}
repro::check_git()
repro::check_github()
repro::check_make()
repro::check_docker()
```
